---
title: "Homework 1"
author: Luna  (Jiying Han)  
output: github_document
---

This is my solution to homework 1


```{r setup}
library(tidyverse)
```

### Problem 1

**1.1 Create a data frame according to the requirement**

```{r prob1_df}
set.seed(1)

prob1_df = 
  tibble(
    samp = rnorm(10), 
    samp_grt_0 = samp > 0,  
    chara_vec = c("e", "f", "g", "h", "i", "j", "k", "l", "m", "n" ),
    fac_vec = factor(c("high", "mid", "high", "low", "low", "low", "high", "mid", "mid",   "mid" )),
)
```

**1.2 Take the mean of each variable**

```{r try_mean}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_grt_0))
mean(pull(prob1_df, chara_vec))
mean(pull(prob1_df, fac_vec))
```


_I can take the mean of "samp", "samp_grt_0", but as for "chara_vec" and "fac_vec", I can't.  
Therefore, I can take the mean of number, logical, but factors and characters can't._

**1.3 Convert to numeric**

```{r eval = FALSE}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_grt_0))
as.numeric(pull(prob1_df, chara_vec))
as.numeric(pull(prob1_df, fac_vec))
```

**1.4 Convert and multiply**

```{r}
as.numeric(pull(prob1_df, samp_grt_0))*pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_grt_0))*pull(prob1_df, samp)
log_vec_asf = as.factor(pull(prob1_df, samp_grt_0))
as.numeric(log_vec_asf)*pull(prob1_df, samp)
```



### Problem 2

```{r}
data("penguins", package = "palmerpenguins")
```

**2.1 Description of the dataset**

_The data in this dataset, including,_

  `r names(penguins)` important variables.
    
    
   Species has `r levels(pull(penguins,species))`.  
   Island incudes `r levels(pull(penguins,island))`.  
   Bill length range is (`r range(pull(penguins,bill_length_mm), na.rm = TRUE)`).  
   Bill depth range is (`r range(pull(penguins,bill_depth_mm), na.rm = TRUE)`).  
   Flipper length range is (`r range(pull(penguins,flipper_length_mm), na.rm = TRUE)`).  
   Body mass range is (`r range(pull(penguins,body_mass_g), na.rm = TRUE)`).  
   Sex includes `r levels(pull(penguins,sex))`.  
   Year range is (`r range(pull(penguins,year), na.rm = FALSE)`).  
   The size of the dataset is `r nrow(penguins)` rows and `r ncol(penguins)` columns.  
   The mean of flipper length is `r mean(pull(penguins, flipper_length_mm) , na.rm = TRUE)`. 


**2.2 Make a scatterplot of flipper_length_mm (y) vs bill_length_mm (x)**


```{r}
library(ggplot2)
set.seed(1)

ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm,  color = species)) + geom_point()
ggsave("penguins_scatterplot.pdf", height = 6, width = 6)
```

**Homework 1 done!! so exciting! this is my first plot done by R. Thank you so much Dr.Jeffrey~**