---
title: "Homework 1"
author: Luna  (Jiying Han)  jh4324
output: github_document
---

This is my solution to homework 1


```{r setup}
library(tidyverse)
```

### Problem 1

* create a data frame according to the requirement

```{r prob1_df}
prob1_df = 
  tibble(
    samp = rnorm(10), 
    samp_grt_0 = samp > 0,  
    chara_vec = c("e", "f", "g", "h", "i", "j", "k", "l", "m", "n" ),
    fac_vec = factor(c("high", "mid", "high", "low", "low", "low", "high", "mid", "mid",   "mid" )),
)
```

* take the mean of each variable

```{r try_mean}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_grt_0))
mean(pull(prob1_df, chara_vec))
mean(pull(prob1_df, fac_vec))
```

I can take the mean of samp, samp_grt_0, but as for chara_vec and fac_vec, I can't.

Therefore, I can take the mean of number, logical, but I can't take if from factors or characters.


* convert to numeric

```{r eval = FALSE}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_grt_0))
as.numeric(pull(prob1_df, chara_vec))
as.numeric(pull(prob1_df, fac_vec))
```


* convert and multiply

```{r}
as.numeric(pull(prob1_df, samp_grt_0))*pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_grt_0))*pull(prob1_df, samp)
log_vec_asf = as.factor(pull(prob1_df, samp_grt_0))
as.numeric(log_vec_asf)*pull(prob1_df, samp)
```



### Problem 2

```{r}
data("penguins", package = "palmerpenguins")
```

* Description of the dataset

The data in this dataset, including,

  `r names(penguins)` important variables.
    
    
   Species has `r levels(pull(penguins,species))`.  
   Island incudes `r levels(pull(penguins,island))`.  
   Bill length range is (`r range(pull(penguins,bill_length_mm), na.rm = TRUE)`).  
   Bill depth range is (`r range(pull(penguins,bill_depth_mm), na.rm = TRUE)`).  
   Flipper length range is (`r range(pull(penguins,flipper_length_mm), na.rm = TRUE)`).  
   Body mass range is (`r range(pull(penguins,body_mass_g), na.rm = TRUE)`).  
   Sex includes `r levels(pull(penguins,sex))`.  
   Year range is (`r range(pull(penguins,year), na.rm = FALSE)`).  
   The size of the dataset is `r nrow(penguins)` rows and `r ncol(penguins)` columns.  
   The mean of flipper length is `r mean(pull(penguins, flipper_length_mm) , na.rm = TRUE)`.


